Intentional release of native species undermines ecological stability

### 2022-09-29 rmd/manuscript.Rmd
Squashed commit of the following:
commit c274913bbbf475b2379bfd5ff5714134b1c4d743
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Sep 14 12:52:06 2022 -0400

    edit: rmd misc

commit b83fa58b0ac121cf4f89fff102048b2ff07a3b1e
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:49 2022 -0400

    Update mcmc_trace_reg.pdf

commit 184921982330ea83d449b2fe44159659f9c52210
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:45 2022 -0400

    edit: misc

commit aaac7131a165551933b99ae948f54d710a673206
Author: aterui <hanabi0111@gmail.com>
Date:   Wed Aug 17 18:21:32 2022 -0

---
title: "Intentional release of native species undermines ecological stability"
output:
  pdf_document:
    latex_engine: xelatex
  #word_document:
  # reference_docx: word_format.docx
csl: pnas.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile, encoding = encoding, output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
---

@@

# setup
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse)
op <- function(x, d = 2) sprintf(paste0("%1.", d, "f"), x)

# theory ####
load(here::here("result/result_ricker.RData"))

n_sim <- sim_result %>% 
  mutate(n_sim = n_warmup + n_burnin + n_timestep) %>% 
  pull(n_sim) %>% 
  unique()

param_set <- sim_result %>% 
  distinct(n_species,
           k,
           r_type,
           r1,
           r_min,
           r_max,
           sd_env,
           phi,
           int_type,
           alpha,
           model,
           seed)

# empirical data ####
source(here::here("code/data_fmt_fishdata.R"))
source(here::here("code/data_fmt_analysis.R"))

df_area <- d0 %>% 
  group_by(site_id, year) %>% 
  summarize(area = unique(area))

filename <- list.files(path = here::here("result"), full.names = T) %>% 
  as_tibble() %>% 
  filter(str_detect(string = .$value, pattern = "reg")) %>% 
  filter(!str_detect(string = .$value, pattern = "reg_rich")) %>% 
  pull()

df_beta <- lapply(filename, function(x) {
  read_csv(here::here(x)) %>% 
    filter(parameter == "b[2]")
})
names(df_beta) <- str_extract(filename, "all|masu|other")

## ssm estimate
df_bp <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
  as_tibble() %>% 
  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
  pull() %>% 
  lapply(function(x) {
    read_csv(x) %>% 
      filter(param == "bp_value") %>% 
      select(mean) %>% 
      mutate(group = str_extract(x, "all|masu|other"))
  }) %>% 
  bind_rows()

## mcmc sample size
df_mcmc_ssm <- list.files(path = here::here("data_fmt"), full.names = T) %>% 
  as_tibble() %>% 
  filter(str_detect(string = .$value, pattern = "ssm")) %>% 
  pull() %>% 
  lapply(function(x) {
    read_csv(x) %>% 
      select(n_total_mcmc,
             n_sample,
             n_thin,
             n_burn) %>% 
      distinct()
  }) %>% 
  bind_rows()

df_mcmc_reg <- list.files(path = here::here("result"), full.names = T) %>% 
  as_tibble() %>% 
  filter(str_detect(string = .$value, pattern = "reg_")) %>% 
  filter(!str_detect(string = .$value, pattern = "rich")) %>% 
  pull() %>% 
  lapply(function(x) {
    read_csv(x) %>% 
      select(n_total_mcmc,
             n_sample,
             n_thin,
             n_burn) %>% 
      distinct()
  }) %>% 
  bind_rows()

## release data
source(here::here("code/data_fmt_stock.R"))

df_stock_stage <- df_stock %>% 
  group_by(release_stage) %>% 
  summarize(stock = sum(abundance)) %>% 
  mutate(ratio = stock / max(stock),
         prop = stock / sum(stock))

@@

$$
N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp\left[r_i\left(1-\frac{N_{i,t}+\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i}\right)\right]~exp(\epsilon_{i,t})
$$

>>>>

---
title: "Intentional release of native species undermines ecological stability"
output:
  #bookdown::pdf_document2:
  #  latex_engine: xelatex
  bookdown::word_document2:
   reference_docx: word_format.docx
csl: pnas.csl
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
bibliography: reference.bib
fontsize: 11pt
header-includes:
  - \usepackage{lineno}
  - \linenumbers
---

@@

suppressMessages(source(here::here("code/set_rmd.R")))

@@

$$
N_{i,t+1} = (N_{i,t}+\phi_i R_t)~exp\left[r_i\left(1-\frac{\alpha_{i1} R_t + \sum_{j=1}^S \alpha_{ij}N_{j,t}}{K_i}\right)\right]~exp(\epsilon_{i,t})
$$
